Tomographic measurement of the intergalactic gas pressure through galaxy-tSZ cross-correlations

### 2019-09-20 notes/paper/paper.tex
updated after paper on arXiv

%\usepackage{widetext}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{bm}
\usepackage{amssymb,amsmath,bm}  
\usepackage{color}
\usepackage[colorlinks,linkcolor=red,citecolor=blue,urlcolor=blue ]{hyperref}
\usepackage{multirow}
\usepackage[utf8]{inputenc}
\usepackage{balance}
\usepackage{enumitem}
\usepackage{lipsum}
\usepackage{ulem}

\newcommand{\nv}{\hat{\boldsymbol{\theta}}}
\newcommand{\wisc}{WI$\times$SC}
\newcommand{\cites}{{\bf CITES}}
\newcommand{\todo}[1]{{\bf TODO:} #1}
\newcommand{\kalo}{Karhunen-Lo\`{e}ve\,}
\newcommand{\jcap}{JCAP}
\newcommand{\mnras}{MNRAS}
\newcommand{\aap}{A\&A}
\newcommand{\aaps}{A\&AS}
\newcommand{\apjs}{ApJS}
\newcommand{\apj}{ApJ}
\newcommand{\apjl}{ApJL}
\newcommand{\prd}{Phys.~Rev.~D}
\newcommand{\prl}{Phys.~Rev.~Lett.}
\newcommand{\aj}{Astron. Journal}
\newcommand{\pasp}{Publications of the ASP}
\newcommand{\nar}{New Astronomy Review}
\newcommand{\procspie}{Proceedings of the SPIE}
\newcommand{\physrep}{Physics Reports}
\newcommand{\baas}{Bulletin of the AAS}
\newcommand{\araa}{Annual Review of Astron and Astrophys}

\newcommand{\MB}[1]{\textcolor{red}{#1}}
\newcommand{\DA}[1]{\textcolor{blue}{#1}}

@@

\section{Introduction}\label{sec:intro}
  Modern observational cosmology has reached a stage where constraints from most current and future datasets are limited by astrophysical systematic uncertainties, i.e. our lack of detailed understanding of the small-scale physics behind the luminous components of the Universe, galaxies and gas \citep[e.g.][]{2011MNRAS.415.3649V,2011MNRAS.417.2020S,2014JCAP...04..028F,2015MNRAS.454.2451E,2015MNRAS.454.1958M,2015JCAP...12..049S,2019MNRAS.488.1652H,2019JCAP...03..020S,2019OJAp....2E...4C}. The limiting factor for cosmological constraints from cluster number counts is the uncertainty in the mass-observable relation \citep{2009ApJ...692.1060V,2010ApJ...722.1180V,2011ApJ...732...44S,2013JCAP...07..008H,2014MNRAS.440.2077M,2014A&A...571A..20P,2015MNRAS.446.2205M,2016A&A...594A..24P,2016ApJ...832...95D,2019ApJ...878...55B}. Cosmic shear measurements are strongly affected by sub-grid baryonic physics, and by uncertainties in the processes by which galaxies acquire correlated intrinsic alignments \citep[e.g.][]{2001MNRAS.320L...7C,2002MNRAS.332..788M,2004PhRvD..70f3526H,2017MNRAS.465.2033J,2018PhRvD..98d3528T,2018arXiv181206076H,2018ARA&A..56..393M,2018arXiv181106989S}. Understanding the impact of baryons on the matter power spectrum requires better knowledge of the distribution of gas in haloes. Finally, even though the clustering pattern of galaxies is one of the cosmological observables with the highest signal-to-noise ratio, the cosmological constraints that can be extracted from it are severely limited by our incomplete understanding of the galaxy-dark matter connection \citep[see e.g.][and references therein]{2018ARA&A..56..435W}. Even the analysis of the temperature anisotropies in the Cosmic Microwave Background (CMB), arguably the cleanest cosmological observable, are currently limited by the impact of astrophysical foregrounds on small scales \citep{2014ApJ...782...74H,2017JCAP...06..031L,2019arXiv190712875P}.

  The CMB secondary anisotropies, in particular the thermal and kinetic Sunyaev-Zeldovich effects \citep[tSZ and kSZ respectively,][]{1972CoASP...4..173S}, as well as the gravitational lensing of CMB photons, have gained popularity as a means to address these issues \citep{2017JCAP...11..040B,2019BAAS...51c.297B}. These effects are relatively clean probes of some of the physical quantities that need to be understood in order to mitigate the impact of astrophysical uncertainties: the matter and gas densities, the gas pressure, and the velocity field. Since these observables are also sensitive to cosmology, their combination with large-scale structure data can be extremely powerful at disentangling astrophysical and cosmological parameters. This has been explored by a large number of groups: CMB lensing data have been used to constrain the bias of different tracers of the matter distribution \citep[e.g.][]{2019MNRAS.485.1720H,2018JCAP...04..053A,2018arXiv181002322A,2018MNRAS.481.1133P}, as well as to calibrate the measurement of galaxy shapes in cosmic shear analyses \citep{2019PhRvD.100b3541A}. The tSZ effect has been used in cross-correlation with galaxy clustering and weak lensing data to determine the physical properties of the diffuse gas, as well as to potentially improve constraints on the amplitude of matter fluctuations \citep{2014PhRvD..89b3508V,2014JCAP...02..030H,2015JCAP...09..046M,2017MNRAS.471.1565H,2017ApJ...845...71A,2018PhRvD..97f3514A,2018MNRAS.480.3928M,2019A&A...624A..48D,2019MNRAS.483..223T,2019arXiv190306654T,2019arXiv190413347P,2019arXiv190707870M}. The kSZ has been used in cross-correlation with galaxy clustering to constrain the growth of structure and the gas density profile around haloes \citep{2016PhRvD..93h2002S,2016A&A...586A.140P,2016PhRvL.117e1301H,2016MNRAS.461.3172S,2017JCAP...03..008D}.

  In this work we focus on the cross-correlation between galaxy clustering data and maps of the tSZ Compton-$y$ parameter, making use of existing data from the \planck\ collaboration \citep{2016A&A...594A..22P} and a set of photometric galaxy surveys \citep{2014ApJS..210....9B,2016ApJS..225....5B}. The availability of redshift information allows us to place constraints on the cosmic evolution of the thermal gas pressure and the thermal energy in haloes, as well as to examine any redshift dependence of the mass bias for tSZ cluster studies. This is a relevant topic given the current mild tensions between SZ cluster number counts and CMB primary anisotropies \citep{2016A&A...594A..24P,2016ApJ...832...95D,2019ApJ...878...55B,2019arXiv190407887Z}, which could be caused by the assumptions made to model the $y$-mass relation. Conversely, under the assumption that the relation between mass and gas pressure is well understood, the tSZ effect can be thought of as a mass tracer, which can be used to break degeneracies with the galaxy bias parameter -- we however leave this analysis for future work.

@@

    \subsubsection{Galaxies and the halo occupation distribution}\label{sssec:theory.hm.hod}
      To model the galaxy overdensity, $\Delta_g$, we use a Halo Occupation Distribution (HOD) model \citep{2002ApJ...575..587B,2005ApJ...633..791Z,2013MNRAS.430..725V}, as prescribed by \cite{2011ApJ...736...59Z}. The HOD models the galaxy content of dark matter haloes as being made up of central and satellite galaxies. Centrals lie at the centre of the halo, while satellites are distributed according to a profile $u_s(r|M)$. Haloes can have zero or one central, and the mean number of centrals for a halo of mass $M$ is modelled as a smoothed step function
      \begin{equation}
        \langle N_c(M)\rangle=\frac{1}{2}\left[1+{\rm erf}\left(\frac{\log(M/M_{\rm min})}{\sigma_{\rm lnM}}\right)\right].
      \end{equation}
      In our fiducial scenario we assume that satellites can only be formed if a halo has a central and has a mass larger than some threshold $M_0$. In that case, the average number of satellites follows a power law of the form:
      \begin{equation}\label{eq:hod1}
        \langle N_s(M)\rangle=N_c(M)\,\Theta(M-M_0)\,\left(\frac{M-M_0}{M_1'}\right)^{\alpha_s}.
      \end{equation}
      For simplicity, we fix $M_0$ to $M_{\rm min}$, $\sigma_{\rm lnM}=0.15$ and $\alpha_s$=1, as in \cite{2018MNRAS.473.4318A}, leaving only two free parameters: $M_{\rm min}$ and $M_1'$. Coupling $M_0$ and $M_{\rm min}$ allows for all haloes containing a central to also contain satellites, and conversely, for all haloes containing satellites to necessarily contain a central. This assumption breaks down in cases such as mergers, where centrals have not been established yet. We however explore departures from the fiducial model.

@@

\section{Data}\label{sec:data}
  \subsection{The Compton-$y$ map}\label{ssec:data.y}
    \begin{figure}
      \centering
      \includegraphics[width=0.5\textwidth]{mask_y.pdf}
      \includegraphics[width=0.5\textwidth]{mask_g.pdf}
      \caption{{\sl Top:} sky mask used for the Compton-$y$ map, corresponding to a sky fraction $f_{\rm sky}=0.59$. {\sl Bottom:} mask used for the 2MPZ and \wisc~ galaxy surveys, corresponding to a sky fraction $f_{\rm sky}=0.68$. The product of both masks leaves a usable sky fraction $f_{\rm sky}\simeq0.58$.
      %The top panel shows, in turquoise, the regions masked additionally when removing sky patches around the position of the tSZ sources detected by \planck\ above 6$\sigma$.
      }
      \label{fig:msk}
    \end{figure}
    We make use of the Compton-$y$ parameter maps made public by the \planck\ collaboration \citep{2016A&A...594A..22P}. These maps were generated using different flavours of the Internal Linear Combination method \citep{2004ApJ...612..633E,2008arXiv0811.4277V}. In a simplified description, the ILC technique selects the linear combination of all frequency channels that preserves the spectrum of the source one wishes to map, minimising the map-level variance. The refined versions of the ILC method used by \planck\ further optimise the linear weights on different scales and different regions of the map, and project out sources with known spectra that are likely to cause significant contamination. In particular, \planck\ has released two $y$ maps, extracted using the MILCA \citep{2013A&A...558A.118H} and NILC \citep{2011MNRAS.410.2481R} variations of the ILC technique. Both methods deproject CMB contamination through its well-known spectrum, but differ on the methods used to calculate the optimal scale-dependent and spatially-varying linear weights.

    The MILCA and NILC maps have been found to be in good agreement in different studies, although the NILC map has a higher noise level on large scales \citep{2016A&A...594A..22P}. We thus use the MILCA map as our fiducial Compton-$y$ map, but repeat our analysis on the NILC map as part of our systematics analysis. We use a fiducial mask for the $y$ maps based on a combination of the \planck\ 60\% Galactic mask and the union of the HFI and LFI point source masks (see top panel of Fig.\!~\ref{fig:msk}).
    %As part of our study of the mass dependence of the signal on halo mass, we additionally mask out all tSZ sources detected by \planck\ above 6$\sigma$, based on the Union catalogue of \cite{2016A&A...594A..27P}.

@@

    Both 2MPZ and WISC suffer from different levels of contamination from Galactic and observational systematics. The most relevant Galactic systematic is star contamination, particularly for \wisc~ \citep{2018arXiv181208182X}. Besides avoiding regions of high dust and star contamination using the sky mask described in \cite{2018MNRAS.481.1133P} (see bottom panel of Fig.\!~\ref{fig:msk}), we correct for the effects of stellar contamination by correcting for a smooth non-linear relation between galaxy and star density (also described in \citejap{2018MNRAS.481.1133P}). After doing so, three potential sources of systematic uncertainty remain: residual stellar contamination, modulation of the galaxy density due to Galactic dust reddening and modulation due to zero-point fluctuations in the photographic plates used by SuperCOSMOS. We address the first two (dust and stars) by deprojecting them at the map level as described in Section \ref{sssec:methods.syst.deproj}. We address the contamination from fluctuations in the SuperCOSMOS plates by modelling it at the power spectrum level, which we describe in Section \ref{sssec:methods.syst.plates}.

@@

      \begin{figure}
        \centering
        \includegraphics[width=0.48\textwidth]{cl_syst_summary.pdf}
        \caption{Summary of the different sources of systematic contamination affecting the galaxy auto-correlations for the particular case of the third \wisc~bin. The red and blue points show the measurements before and after deprojecting a dust and a star template, while the grey dashed line shows the best-fit contamination from SuperCOSMOS plate fluctuations assuming no intrinsic clustering. The solid black line shows the best-fit theory model. The light grey bands indicate the data points removed due to scale cuts.}
        \label{fig:clsyst}
      \end{figure}

@@

      The contamination from plate fluctuations can therefore be accounted for as an additive contribution to the model describing the galaxy auto-spectrum, proportional to a template $T_\ell\equiv|W_\ell|^2$ with a free amplitude $A\equiv S_{\rm plate}\sigma_{\rm plate}^2$ that is marginalised over. Since $A$ is a linear parameter, this can be done analytically in a pre-processing step by modifying the inverse covariance matrix of the galaxy auto-spectra as follows \citep{1992ApJ...398..169R}:
      \begin{equation}
        {\sf Cov}^{-1}\hspace{6pt}\rightarrow\hspace{6pt} {\sf Cov}^{-1}-\frac{{\sf Cov}^{-1}{\bf T}\cdot{\bf T}^T{\sf Cov}^{-1}}{{\bf T}^T{\sf Cov}^{-1}{\bf T}},
      \end{equation}
      where ${\bf T}$ is a vector containing the template $T_\ell$ for all the scales used in the analysis. Fig.\!~\ref{fig:clsyst} shows the shape of the plate template $T_\ell$ normalised by the best-fit value of the parameter $A$ assuming no intrinsic clustering.

    \subsubsection{Scale cuts}\label{sssec:methods.syst.scales}
      After deprojecting dust and stars at the map level, and the imprint of the SuperCOSMOS plates at the power spectrum level, we still observe an unacceptably large amount of power on scales $\ell<10$ in all galaxy auto-correlations involving \wisc. These may be due to residual star contamination that is not simply removed with a linear template \citep{2018arXiv181208182X}, or inaccuracies in our treatment of the SuperCOSMOS fluctuations. To avoid biasing our results we therefore remove the lowest bandpower from all galaxy auto-correlations involving \wisc.

@@

      Another possible source of systematic uncertainty is the effect of biased photometric redshifts (i.e. where $\langle z|z_{\rm photo}\rangle\neq z_{\rm photo}$). The {\tt ANNz} method used in \cite{2018MNRAS.481.1133P} should guarantee unbiased photo-$z$'s, but this can never be achieved exactly in practice. It would be possible to account for this form of uncertainty by treating $\bar{z}$ as a free parameter, as is usually done in photometric cosmic shear analyses. Our results, however, are more sensitive to the distribution widths, and we find that this simple parametrisation is able to describe our data sufficiently well. We leave a more detailed analysis of the associated photometric redshift systematics for future work.

@@

      \begin{figure*}
        \centering
        \includegraphics[width=0.6\textwidth]{fiducial_wisc3.pdf}
        \caption{68\% and 95\% contours for the model parameters in the third WI$\times$SC redshift bin.}
        \label{fig:triangle}
      \end{figure*}

      \begin{figure*}
        \centering
        \includegraphics[width=0.7\textwidth]{bhydro.pdf}
        \caption{Summary figure showing our constraints on the tSZ mass bias $1-\bH$. Our fiducial constrains are shown as black circles with error bars, and are centred at the mean redshift of each sample. The grey circles show the same constraints found using the NILC $y$ map, which are in good agreement with our fiducial results. The red downward-pointing triangles show the constraints found fixing the photo-$z$ width parameter, $w_z$. They are in good agreement with our fiducial measurements, with $\sim20\%$ smaller error bars. The burgundy squares show the results found using the 2010 Tinker mass function, which are systematically biased low. The orange diamond and the mesh show our combined, redshift-independent constraint on $1-\bH$. For comparison, the grey and turquoise bands show the constraints on the mass bias found by combining cluster counts and CMB primary \citep{2016A&A...594A..24P} as well as the constraints using CMB lensing to calibrate cluster masses \citep{2019arXiv190407887Z}, respectively. The top panel shows the normalised redshift distributions for the six redshift bins, for reference.}
        \label{fig:bh}
      \end{figure*}

@@

      The corresponding constraints on $1-\bH$ for all redshift bins are shown in the main panel of Fig.\!~\ref{fig:bh} as black circles with error bars. The values shown in the figure and given explicitly in column 4 of Table \ref{tab:results} correspond to the peak of the 1-dimensional distribution of $1-\bH$ and to the equal-probability values encompassing a total probability of 0.68 (1$\sigma$). The maximum-likelihood value of $1-\bH$ is provided in column 3 of the same Table. Columns 6 and 7 list the reduced $\chi^2$ values for each sample and their associated probability-to-exceed (PTE), respectively. In all cases we find that the model described in Section \ref{sec:theory} is able to describe the data with no evidence for a significant statistical tension. The top panel of Fig.\!~\ref{fig:bh} shows the normalised redshift distributions of the different bins used in this analysis, and can be used to visually assess the level of correlation between the different measurements.

@@

      Our results are in broad agreement with the estimate of a redshift-independent $1-\bH$ found by \cite{2019arXiv190407887Z} by calibrating cluster masses with CMB lensing ($1-\bH=0.71\pm0.1$), shown in Fig.\!~\ref{fig:bh} as a turquoise semi-transparent band. In turn, the grey band in the same figure shows the constraints on $1-\bH$ found by combining tSZ cluster counts and the $TT$ CMB power spectrum measured by \planck\ \citep{2016A&A...594A..24P} ($1-\bH=0.58\pm0.04$). This is the value of $1-\bH$ needed to simultaneously explain the amplitude of density perturbations predicted by the CMB and the abundance of massive clusters. Our measurements are visually in agreement with both of these estimates, which themselves are not in significant tension with one another.

>>>>

\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{bm}
\usepackage{amssymb,amsmath,bm}  
\usepackage{color}
\usepackage[colorlinks,linkcolor=red,citecolor=blue,urlcolor=blue ]{hyperref}
\usepackage{multirow}
\usepackage[utf8]{inputenc}
\usepackage{balance}
\usepackage{enumitem}
\usepackage{lipsum}
\usepackage{ulem}

\newcommand{\nv}{\hat{\boldsymbol{\theta}}}
\newcommand{\wisc}{WI$\times$SC}
\newcommand{\kalo}{Karhunen-Lo\`{e}ve\,}
\newcommand{\jcap}{JCAP}
\newcommand{\mnras}{MNRAS}
\newcommand{\aap}{A\&A}
\newcommand{\aaps}{A\&AS}
\newcommand{\apjs}{ApJS}
\newcommand{\apj}{ApJ}
\newcommand{\apjl}{ApJL}
\newcommand{\prd}{Phys.~Rev.~D}
\newcommand{\prl}{Phys.~Rev.~Lett.}
\newcommand{\aj}{Astron. Journal}
\newcommand{\pasp}{Publications of the ASP}
\newcommand{\nar}{New Astronomy Review}
\newcommand{\procspie}{Proceedings of the SPIE}
\newcommand{\physrep}{Physics Reports}
\newcommand{\baas}{Bulletin of the AAS}
\newcommand{\araa}{Annual Review of Astron and Astrophys}

@@

\section{Introduction}\label{sec:intro}
  Modern observational cosmology has reached a stage where constraints from most current and future datasets are limited by astrophysical systematic uncertainties, i.e. our lack of detailed understanding of the small-scale physics behind the luminous components of the Universe, galaxies and gas \citep[e.g.][]{2011MNRAS.415.3649V,2011MNRAS.417.2020S,2014JCAP...04..028F,2015MNRAS.454.2451E,2015MNRAS.454.1958M,2015JCAP...12..049S,2019MNRAS.488.1652H,2019JCAP...03..020S,2019OJAp....2E...4C}. The limiting factor for cosmological constraints from cluster number counts is the uncertainty in the mass-observable relation \citep{2009ApJ...692.1060V,2010ApJ...722.1180V,2011ApJ...732...44S,2013JCAP...07..008H,2014MNRAS.440.2077M,2014A&A...571A..20P,2015MNRAS.446.2205M,2016A&A...594A..24P,2016ApJ...832...95D,2019ApJ...878...55B}. Cosmic shear measurements are strongly affected by sub-grid baryonic physics, and by uncertainties in the processes by which galaxies acquire correlated intrinsic alignments \citep[e.g.][]{2001MNRAS.320L...7C,2002MNRAS.332..788M,2004PhRvD..70f3526H,2017MNRAS.465.2033J,2018PhRvD..98d3528T,2018arXiv181206076H,2018ARA&A..56..393M,2019MNRAS.tmp.2187S}. Understanding the impact of baryons on the matter power spectrum requires better knowledge of the distribution of gas in haloes. Finally, even though the clustering pattern of galaxies is one of the cosmological observables with the highest signal-to-noise ratio, the cosmological constraints that can be extracted from it are severely limited by our incomplete understanding of the galaxy-dark matter connection \citep[see e.g.][and references therein]{2018ARA&A..56..435W}. Even the analysis of the temperature anisotropies in the Cosmic Microwave Background (CMB), arguably the cleanest cosmological observable, are currently limited by the impact of astrophysical foregrounds on small scales \citep{2014ApJ...782...74H,2017JCAP...06..031L,2019arXiv190712875P}.

  The CMB secondary anisotropies, in particular the thermal and kinetic Sunyaev-Zeldovich effects \citep[tSZ and kSZ respectively,][]{1972CoASP...4..173S}, as well as the gravitational lensing of CMB photons, have gained popularity as a means to address these issues \citep{2017JCAP...11..040B,2019BAAS...51c.297B}. These effects are relatively clean probes of some of the physical quantities that need to be understood in order to mitigate the impact of astrophysical uncertainties: the matter and gas densities, the gas pressure, and the velocity field. Since these observables are also sensitive to cosmology, their combination with large-scale structure data can be extremely powerful at disentangling astrophysical and cosmological parameters. This has been explored by a large number of groups: CMB lensing data have been used to constrain the bias of different tracers of the matter distribution \citep[e.g.][]{2019MNRAS.485.1720H,2018JCAP...04..053A,2019PhRvD.100b3541A,2018MNRAS.481.1133P}, as well as to calibrate the measurement of galaxy shapes in cosmic shear analyses \citep{2019PhRvD.100b3541A}. The tSZ effect has been used in cross-correlation with galaxy clustering and weak lensing data to determine the physical properties of the diffuse gas, as well as to potentially improve constraints on the amplitude of matter fluctuations \citep{2014PhRvD..89b3508V,2014JCAP...02..030H,2015JCAP...09..046M,2017MNRAS.471.1565H,2017ApJ...845...71A,2018PhRvD..97f3514A,2018MNRAS.480.3928M,2019A&A...624A..48D,2019MNRAS.483..223T,2019arXiv190306654T,2019arXiv190413347P,2019arXiv190707870M}. The kSZ has been used in cross-correlation with galaxy clustering to constrain the growth of structure and the gas density profile around haloes \citep{2016PhRvD..93h2002S,2016A&A...586A.140P,2016PhRvL.117e1301H,2016MNRAS.461.3172S,2017JCAP...03..008D}.

  In this work we focus on the cross-correlation between galaxy clustering data and maps of the tSZ Compton-$y$ parameter, making use of existing data from the \planck\ collaboration \citep{2016A&A...594A..22P} and a set of photometric galaxy surveys \citep{2014ApJS..210....9B,2016ApJS..225....5B}. The availability of redshift information allows us to place constraints on the cosmic evolution of the thermal gas pressure and the thermal energy in haloes, as well as to examine any redshift dependence of the mass bias for tSZ cluster studies. This is a relevant topic given the current mild tensions between SZ cluster number counts and CMB primary anisotropies \citep{2016A&A...594A..24P,2016ApJ...832...95D,2019ApJ...878...55B,2019MNRAS.489..401Z}, which could be caused by the assumptions made to model the $y$-mass relation. Conversely, under the assumption that the relation between mass and gas pressure is well understood, the tSZ effect can be thought of as a mass tracer, which can be used to break degeneracies with the galaxy bias parameter -- we however leave this analysis for future work.

@@

    \subsubsection{Galaxies and the halo occupation distribution}\label{sssec:theory.hm.hod}
      To model the galaxy overdensity, $\Delta_g$, we use a Halo Occupation Distribution (HOD) model \citep{2002ApJ...575..587B,2005ApJ...633..791Z,2013MNRAS.430..725V}, as prescribed by \cite{2011ApJ...736...59Z}. The HOD models the galaxy content of dark matter haloes as being made up of central and satellite galaxies. Centrals lie at the centre of the halo, while satellites are distributed according to a profile $u_s(r|M)$. Haloes can have zero or one central, and the mean number of centrals for a halo of mass $M$ is modelled as a smoothed step function
      \begin{equation}
        \langle N_c(M)\rangle=\frac{1}{2}\left[1+{\rm erf}\left(\frac{\log(M/M_{\rm min})}{\sigma_{\rm lnM}}\right)\right].
      \end{equation}
      In our fiducial scenario we assume that satellites can only be formed if a halo has a central and has a mass larger than some threshold $M_0$. In that case, the average number of satellites follows a power law of the form:
      \begin{equation}\label{eq:hod1}
        \langle N_s(M)\rangle=N_c(M)\,\Theta(M-M_0)\,\left(\frac{M-M_0}{M_1'}\right)^{\alpha_s}.
      \end{equation}
      For simplicity, we fix $M_0$ to $M_{\rm min}$, $\sigma_{\rm lnM}=0.15$ and $\alpha_s$=1, as in \cite{2018MNRAS.473.4318A}, leaving only two free parameters: $M_{\rm min}$ and $M_1'$. Coupling $M_0$ and $M_{\rm min}$ allows for all haloes containing a central to also contain satellites, and conversely, for all haloes containing satellites to necessarily contain a central. This assumption breaks down in cases such as recent major mergers, where centrals may not immediately be established.

@@

\section{Data}\label{sec:data}
  \subsection{The Compton-$y$ map}\label{ssec:data.y}
    \begin{figure}
      \centering
      \includegraphics[width=0.5\textwidth]{mask_y.pdf}
      \includegraphics[width=0.5\textwidth]{mask_g.pdf}
      \caption{{\sl Top:} sky mask used for the Compton-$y$ map, corresponding to a sky fraction $f_{\rm sky}=0.59$. {\sl Bottom:} mask used for the 2MPZ and \wisc~ galaxy surveys, corresponding to a sky fraction $f_{\rm sky}=0.68$. The product of both masks leaves a usable sky fraction $f_{\rm sky}\simeq0.58$.
      }
      \label{fig:msk}
    \end{figure}
    We make use of the Compton-$y$ parameter maps made public by the \planck\ collaboration \citep{2016A&A...594A..22P}. These maps were generated using different flavours of the Internal Linear Combination method \citep{2004ApJ...612..633E,2008arXiv0811.4277V}. In a simplified description, the ILC technique selects the linear combination of all frequency channels that preserves the spectrum of the source one wishes to map, minimising the map-level variance. The refined versions of the ILC method used by \planck\ further optimise the linear weights on different scales and different regions of the map, and project out sources with known spectra that are likely to cause significant contamination. In particular, \planck\ has released two $y$ maps, extracted using the MILCA \citep{2013A&A...558A.118H} and NILC \citep{2011MNRAS.410.2481R} variations of the ILC technique. Both methods deproject CMB contamination through its well-known spectrum, but differ on the methods used to calculate the optimal scale-dependent and spatially-varying linear weights.

    The MILCA and NILC maps have been found to be in good agreement in different studies, although the NILC map has a higher noise level on large scales \citep{2016A&A...594A..22P}. We thus use the MILCA map as our fiducial Compton-$y$ map, but repeat our analysis on the NILC map as part of our systematics analysis. We use a fiducial mask for the $y$ maps based on a combination of the \planck\ 60\% Galactic mask and the union of the HFI and LFI point source masks (see top panel of Fig.\!~\ref{fig:msk}).

@@

    Both 2MPZ and WISC suffer from different levels of contamination from Galactic and observational systematics. The most relevant Galactic systematic is star contamination, particularly for \wisc~ \citep{2019JCAP...08..037X}. Besides avoiding regions of high dust and star contamination using the sky mask described in \cite{2018MNRAS.481.1133P} (see bottom panel of Fig.\!~\ref{fig:msk}), we correct for the effects of stellar contamination by correcting for a smooth non-linear relation between galaxy and star density (also described in \citejap{2018MNRAS.481.1133P}). After doing so, three potential sources of systematic uncertainty remain: residual stellar contamination, modulation of the galaxy density due to Galactic dust reddening and modulation due to zero-point fluctuations in the photographic plates used by SuperCOSMOS. We address the first two (dust and stars) by deprojecting them at the map level as described in Section \ref{sssec:methods.syst.deproj}. We address the contamination from fluctuations in the SuperCOSMOS plates by modelling it at the power spectrum level, which we describe in Section \ref{sssec:methods.syst.plates}.

@@

      \begin{figure}
        \centering
        \includegraphics[width=0.48\textwidth]{cl_syst_summary.pdf}
        \caption{Summary of the different sources of systematic contamination affecting the galaxy auto-correlations for the particular case of the third \wisc~bin. The red and blue points show the measurements before and after deprojecting a dust and a star template. The dot-dashed line shows the best-fit contamination from SuperCOSMOS plate fluctuations that explains the residuals of the data with respect to the best-fit HOD-only model (dashed line). The total combined prediction is shown as the solid line. The light grey bands show our scale cuts.}
        \label{fig:clsyst}
      \end{figure}

@@

      The contamination from plate fluctuations can therefore be accounted for as an additive contribution to the model describing the galaxy auto-spectrum, proportional to a template $T_\ell\equiv|W_\ell|^2$ with a free amplitude $A\equiv S_{\rm plate}\sigma_{\rm plate}^2$ that is marginalised over. Since $A$ is a linear parameter, this can be done analytically in a pre-processing step by modifying the inverse covariance matrix of the galaxy auto-spectra as follows \citep{1992ApJ...398..169R}:
      \begin{equation}
        {\sf Cov}^{-1}\hspace{6pt}\rightarrow\hspace{6pt} {\sf Cov}^{-1}-\frac{{\sf Cov}^{-1}{\bf T}\cdot{\bf T}^T{\sf Cov}^{-1}}{{\bf T}^T{\sf Cov}^{-1}{\bf T}},
      \end{equation}
      where ${\bf T}$ is a vector containing the template $T_\ell$ for all the scales used in the analysis. The dot-dashed line in Fig.\!~\ref{fig:clsyst} shows the shape of the plate template $T_\ell$ normalised by the best-fit value of the parameter $A$ that explains the residuals of the data with respect to the best-fit HOD-only model (shown as a dashed line). The plate fluctuations contribute to $\sim10\%$ of the signal on scales $\ell\lesssim 30$.

    \subsubsection{Scale cuts}\label{sssec:methods.syst.scales}
      After deprojecting dust and stars at the map level, and the imprint of the SuperCOSMOS plates at the power spectrum level, we still observe an unacceptably large amount of power on scales $\ell<10$ in all galaxy auto-correlations involving \wisc. These may be due to residual star contamination that is not simply removed with a linear template \citep{2019JCAP...08..037X}, or inaccuracies in our treatment of the SuperCOSMOS fluctuations. To avoid biasing our results we therefore remove the lowest bandpower from all galaxy auto-correlations involving \wisc.

@@

      Another possible source of systematic uncertainty is the effect of biased photometric redshifts (i.e. where $\langle z|z_{\rm photo}\rangle\neq z_{\rm photo}$). The {\tt ANNz} method used in \cite{2018MNRAS.481.1133P} should guarantee unbiased photo-$z$'s, but this can never be achieved exactly in practice. It would be possible to account for this form of uncertainty by treating $\bar{z}$ as a free parameter, as is usually done in photometric cosmic shear analyses. Our results, however, are more sensitive to the distribution widths, and we find that this simple parameterisation is able to describe our data sufficiently well. We leave a more detailed analysis of the associated photometric redshift systematics for future work.

@@

      \begin{figure*}
        \centering
        \includegraphics[width=0.7\textwidth]{fiducial_wisc3.pdf}
        \caption{68\% and 95\% contours for the model parameters in the third WI$\times$SC redshift bin.}
        \label{fig:triangle}
      \end{figure*}

      \begin{figure*}
        \centering
        \includegraphics[width=0.7\textwidth]{bhydro.pdf}
        \caption{Summary figure showing our constraints on the tSZ mass bias $1-\bH$. Our fiducial constrains are shown as black circles with error bars, and are centred at the mean redshift of each sample. The grey circles show the same constraints found using the NILC $y$ map, which are in good agreement with our fiducial results. The red downward-pointing triangles show the constraints found fixing the photo-$z$ width parameter, $w_z$. They are in good agreement with our fiducial measurements, with $\sim20\%$ smaller error bars. The burgundy squares show the results found using the 2010 Tinker mass function, which are systematically biased low. The orange diamond and the mesh show our combined, redshift-independent constraint on $1-\bH$. For comparison, the grey and turquoise bands show the constraints on the mass bias found by combining cluster counts and CMB primary \citep{2016A&A...594A..24P} as well as the constraints using CMB lensing to calibrate cluster masses \citep{2019MNRAS.489..401Z}, respectively. The top panel shows the normalised redshift distributions for the six redshift bins, for reference.}
        \label{fig:bh}
      \end{figure*}

@@

      The corresponding constraints on $1-\bH$ for all redshift bins are shown in the main panel of Fig.\!~\ref{fig:bh} as black circles with error bars (corresponding to the median and 68\% confidence interval). These results are summarized in Table \ref{tab:results}, where column 3 shows the maximum-likelihood value of $1-\bH$, while column 4 lists the peak of the marginalized 1-dimensional distribution and the confidence interval corresponding to the equal-probability values encompassing a total probability of 0.68. Columns 6 and 7 of the same table list the reduced $\chi^2$ values for each sample and their associated probability-to-exceed (PTE), respectively. In all cases we find that the model described in Section \ref{sec:theory} is able to describe the data with no evidence for a significant statistical tension. The top panel of Fig.\!~\ref{fig:bh} shows the normalised redshift distributions of the different bins used in this analysis, and can be used to visually assess the level of correlation between the different measurements.

@@

      Our results are in broad agreement with the estimate of a redshift-independent $1-\bH$ found by \cite{2019MNRAS.489..401Z} by calibrating cluster masses with CMB lensing ($1-\bH=0.71\pm0.1$), shown in Fig.\!~\ref{fig:bh} as a turquoise semi-transparent band. In turn, the grey band in the same figure shows the constraints on $1-\bH$ found by combining tSZ cluster counts and the $TT$ CMB power spectrum measured by \planck\ \citep{2016A&A...594A..24P} ($1-\bH=0.58\pm0.04$). This is the value of $1-\bH$ needed to simultaneously explain the amplitude of density perturbations predicted by the CMB and the abundance of massive clusters. Our measurements are visually in agreement with both of these estimates, which themselves are not in significant tension with one another.
